Weekly group meetings

### 2023-05-31 diapo/groupTemplate/main.tex
Working on a new template
Changed a bit of the template, not done yet

\documentclass{beamer}
\usetheme{Boadilla}
\usecolortheme{whale}

\usepackage{wrapfig}

\title[MSc Thesis]
{Memristors-based Recurrent Modules for Neural Computing}
%\subtitle{Using }

\institute[IST] % (optional)
{%
  Diogo Caetano\\
  INESC-MN
  \and%
  Ruxandra Barlulescu\\
  INESC-ID
}

\author[V. BARBAZA]{Valentin BARBAZA (MEEC)}

\date[2023] % (optional)
{May 2023}

\logo{\includegraphics[height=0.7cm]{figures/istnewlogo.pdf}}

\definecolor{istblue}{RGB}{0,102,153}
\setbeamercolor{titlelike}{bg=istblue}
\setbeamerfont{title}{series=\bfseries}

@@

%\begin{frame}
%\frametitle{Table of Contents}
%\tableofcontents
%\end{frame}

\begin{frame}
\frametitle{Application/Motivation}
The goal of the thesis is to know whether an analog LSTM network would work. This would allow running a Neural Network in real-time in embedded systems. The analog implementation (using memristors crossbar array) allows for much greater computational speed and very small on-chip area.
\end{frame}
\begin{frame}
\frametitle{Technical Goals}
My point is to run simulations using cadence. Running a working simulation is the first step before fabricating the system.
\end{frame}
\begin{frame}
\frametitle{Progress}
So far, I have designed some smaller elements required for the system to work such as the activation function for example.\\
I've designed a full size LSTM (with 4 hidden state).
\begin{figure}
    \centering
    \includegraphics[height=0.35\textheight]{figures/LSTM.png}
\end{figure}
I am now working on a way to generate LSTM network of any size.
\end{frame}

\begin{frame}
\frametitle{What is missing}
I now need to run the simulations and compare the results of my simulation with the results a digital LSTM (running with Keras for example).
\end{frame}

>>>>

\documentclass[table]{beamer}
\usetheme{Boadilla}
\usecolortheme{whale}

%\usepackage[table]{xcolor}

\title[Group Meeting]
{Weekly group meetings}

\subtitle{Memristors-based recurent modules for neural computing}

\author[V. BARBAZA]{Valentin BARBAZA}

\date[26 May] % (optional)
{26 May 2023}

\logo{\includegraphics[height=0.9cm]{figures/logos.png}}

\definecolor{text}{RGB}{25,116,146}
\definecolor{firstRow}{HTML}{219BC3}
\definecolor{evenRow}{HTML}{CCDEE9}
\definecolor{oddRow}{HTML}{E7EFF4}
\definecolor{istblue}{RGB}{0,102,153}
\setbeamercolor{titlelike}{bg=istblue}
\setbeamerfont{title}{series=\bfseries}

@@

\begin{frame}
  \frametitle{Introduction}
  Quick introduction to your topic.

  \begin{itemize}
      \color{text}
    \item Briefly summarized your project. Some of the attendants may need some refresh.
    \item Explain in which project stage you are, thus we all know how close you are to achieve your goals.
  \end{itemize}

  ex: I have to design a PCB to control a magnetic sensor. I have already done the PCB and now I am testing it.
\end{frame}

\begin{frame}
  \frametitle{Last weeks...}

  Last meeting, I promised to do…

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{3cm} c c c }
    \rowcolor{firstRow}
    & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
    1 & test2 & test23 & test3 & test4\\
    2 & test2 & test23 & test3 & test4\\
    3 & test2 & test23 & test3 & test4\\
    4 & test2 & test23 & test3 & test4\\
    5 & test2 & test23 & test3 & test4\\
  \end{tabular}

\end{frame}

\begin{frame}
  \frametitle{}
\end{frame}
